Austria's Covid legislation: Duration of parliamentarian consultation period in comparision.

### 2021-02-20 _post/2019-11-20-vorzugsstimmen/vorzugsstimmen.Rmd
css backgroud white

```{r echo=FALSE, message=FALSE, warning=TRUE}
df_merge %>% 
  reactable(.,
          filterable = T,
          pagination = T,
          height = 250,
          outlined = T,
          bordered = F,
          compact=T,
          theme=reactableTheme(backgroundColor = plot_bg_color,
                           style=list(fontFamily="Karla",
                                      fontSize="12px"),
                           filterInputStyle = list(
                             color="black",
                             backgroundColor = plot_bg_color)))

@@

```{r message=FALSE, warning=FALSE, paged.print=TRUE, code_folding=NULL, echo=F}
library(reactable)
n_mandates_regional_districts %>% 
  reactable(.,
            filterable = T,
          pagination = T,
          height = 250,
          outlined = T,
          bordered = F,
          compact=T,
          theme=reactableTheme(backgroundColor = plot_bg_color,
                           style=list(fontFamily="Karla",
                                      fontSize="12px"),
                           filterInputStyle = list(
                             color="black",
                             backgroundColor = plot_bg_color)))

>>>>

```{r echo=FALSE, message=FALSE, warning=TRUE, eval=F}
df_merge %>% 
  reactable(.,
          filterable = T,
          pagination = T,
          height = 250,
          outlined = T,
          bordered = F,
          compact=T,
          theme=reactableTheme(backgroundColor = plot_bg_color,
                           style=list(fontFamily="Karla",
                                      fontSize="12px"),
                           filterInputStyle = list(
                             color="black",
                             backgroundColor = plot_bg_color)))

@@

```{r message=FALSE, warning=FALSE, paged.print=TRUE, code_folding=NULL, echo=F, eval=F}
library(reactable)
n_mandates_regional_districts %>% 
  reactable(.,
            filterable = T,
          pagination = T,
          height = 250,
          outlined = T,
          bordered = F,
          compact=T,
          theme=reactableTheme(backgroundColor = plot_bg_color,
                           style=list(fontFamily="Karla",
                                      fontSize="12px"),
                           filterInputStyle = list(
                             color="black",
                             backgroundColor = plot_bg_color)))

### 2021-02-20 _post/2020-07-21-attransperency/attransperency.Rmd
css backgroud white

theme_post <- function() {
  hrbrthemes::theme_ipsum_rc() +
    theme(
      plot.background = element_rect(fill = plot_bg_color, color=NA),
      panel.background = element_rect(fill = plot_bg_color, color=NA),
      plot.margin = margin(l = 0, unit = "cm"),
      plot.title = element_text(
        color = "grey20",
        face = "bold",
        margin = margin(l = 0, unit = "cm"),
        size = 13
      ),
      plot.title.position = "plot",
      plot.subtitle = element_text(
        color = "grey50",
        margin = margin(t = 0.2, b = 0.3, unit = "cm"),
        size = 11
      ),
      plot.caption = element_text(
        color = "grey50",
        size = 8,
        hjust = c(0)
      ),
      plot.caption.position = "panel",
      axis.title.x = element_text(angle = 0,
                                         color="grey50",
                                         hjust=1),
      axis.text.x = element_text(size = 9, 
                                 color = "grey50"),
      axis.title.y = element_blank(),
      axis.text.y = element_text(size = 9,
                                 color="grey50"),
      panel.grid.minor.x = element_blank(),
      panel.grid.major.x = element_blank(),
      panel.grid.minor.y = element_blank(),
      panel.spacing = unit(0.25, "cm"),
      panel.spacing.y = unit(0.25, "cm"),
      strip.text = element_text(
        angle = 0,
        size = 9,
        vjust = 1,
        face = "bold"
      ),
      legend.title = element_text(
        color = "grey30",
        face = "bold",
        vjust = 1,
        size = 7
      ),
      legend.text = element_text(
        size = 7,
        color = "grey30"
      ),
      legend.justification = "left",
      legend.box = "horizontal", # arrangement of multiple legends
      legend.direction = "vertical",
      legend.margin = margin(l = 0, t = 0, unit = "cm"),
      legend.spacing.y = unit(0.07, units = "cm"),
      legend.text.align = 0,
      legend.box.just = "top",
      legend.key.height = unit(0.2, "line"),
      legend.key.width = unit(0.5, "line"),
      text = element_text(size = 3)
    )
}

@@

```{r echo=FALSE, code_folding=F}
datatable(df_income %>% select(name, party, gender, income_category_19),
          colnames=c("MP name"="name", "income category"="income_category_19"),
          filter="top",
          options=list(pageLength=10,
                       columnDefs = list(list(className = 'dt-center', targets = 1:3,
                                         searchable=TRUE))),
          rownames = FALSE)
```

@@

```{r echo=FALSE, code_folding=NULL}
pl_rel
```

>>>>

theme_post <- function() {
  hrbrthemes::theme_ipsum_rc() +
    theme(
      plot.background = element_rect(fill = plot_bg_color, color=NA),
      panel.background = element_rect(fill = plot_bg_color, color=NA),
      plot.margin = margin(l = 0, unit = "cm"),
      plot.title = element_text(
        color = "grey20",
        face = "bold",
        margin = margin(l = 0, unit = "cm"),
        size = 13
      ),
      plot.title.position = "plot",
      plot.subtitle = element_text(
        color = "grey50",
        margin = margin(t = 0.2, b = 0.3, unit = "cm"),
        size = 11
      ),
      plot.caption = element_text(
        color = "grey50",
        size = 8,
        hjust = c(0)
      ),
      plot.caption.position = "panel",
      axis.title.x = element_text(angle = 0,
                                         color="grey50",
                                         hjust=1),
      axis.text.x = element_text(size = 9, 
                                 color = "grey50"),
      axis.title.y = element_blank(),
      axis.text.y = element_text(size = 9,
                                 color="grey50"),
      panel.grid.minor.x = element_blank(),
      panel.grid.major.x = element_blank(),
      panel.grid.minor.y = element_blank(),
      panel.spacing = unit(0.25, "cm"),
      panel.spacing.y = unit(0.25, "cm"),
      strip.text = element_text(
        angle = 0,
        size = 9,
        vjust = 1,
        face = "bold"
      ),
      legend.title = element_text(
        color = "grey30",
        face = "bold",
        vjust = 1,
        size = 7
      ),
      legend.text = element_text(
        size = 7,
        color = "grey30"
      ),
      legend.justification = "left",
      legend.box = "horizontal", # arrangement of multiple legends
      legend.direction = "vertical",
      legend.margin = margin(l = 0, t = 0, unit = "cm"),
      legend.spacing.y = unit(0.07, units = "cm"),
      legend.text.align = 0,
      legend.box.just = "top",
      legend.key.height = unit(0.2, "line"),
      legend.key.width = unit(0.5, "line"),
      text = element_text(size = 5)
    )
}

@@

```{r echo=FALSE, code_folding=NULL}
datatable(df_income %>% select(name, party, gender, income_category_19),
          colnames=c("MP name"="name", "income category"="income_category_19"),
          filter="top",
          options=list(pageLength=10,
                       columnDefs = list(list(className = 'dt-center', targets = 1:3,
                                         searchable=TRUE))),
          rownames = FALSE)
```

@@

```{r echo=FALSE, fig.height=7, fig.width=10, code_folding=NULL, dev="svglite"}
pl_rel
```

### 2021-02-20 _post/2020-12-22-submissionsepidemiclaw/submissionsepidemiclaw.Rmd
update format post similarity
css backgroud white

```{r echo=FALSE, paged.print=TRUE}
reactable(df_submission, 
          defaultPageSize = 4, 
          columns = list(
            link_single_submission_page = colDef(
              cell = function(value) {
                url <- value
                htmltools::tags$a(href = url, 
                                  target = "_blank", 
                                  value)
                },
              width = 150,
              html=TRUE
              )),
          filterable = TRUE,
          bordered=TRUE,
          compact = TRUE,
          style = list(fontSize = "10px"),
          theme = reactableTheme(
            backgroundColor = "#f0eff0",
                filterInputStyle = list(
                  color="green",
                  backgroundColor = "#f0eff0")))
```

@@

```{r include=FALSE}
df_submission <- readr::read_rds(file="submissionsepidemiclaw_files/df_submission_150.rds")

@@

```{r}
tb_text <- reactable(df_submission %>%
            filter(pattern_indicator==TRUE) %>% 
            select(name, date, doc_text),
          defaultPageSize = 4, 
          filterable = TRUE,
          style = list(fontSize = "10px"),
          columns=list(
            name=colDef(width=100),
            date=colDef(width=100),
            doc_text=colDef(minWidth=200)),
          bordered=TRUE,
          compact = TRUE,
          theme = reactableTheme(
            backgroundColor = "#f0eff0",
                filterInputStyle = list(
                  color="green",backgroundColor = "#f0eff0")
          )
          )

@@

```{r echo=FALSE}
reactable(df_collocs,
          bordered=TRUE,
          compact = TRUE,
          style = list(fontSize = "10px"),
          filterable = TRUE,
          theme = reactableTheme(
            backgroundColor = "#f0eff0",
                filterInputStyle = list(
                  color="green",
                  backgroundColor = "#f0eff0")))
```

@@

```{r echo=FALSE}
reactable(head(df_similarity, n = 10^3),
          columns=list(
            cosine=colDef(format=colFormat(digits=4),
                          align="left")),
          bordered=TRUE,
          compact = TRUE,
          style = list(fontSize = "10px"),
          filterable = TRUE,
          theme = reactableTheme(
            backgroundColor = "#f0eff0",
                filterInputStyle = list(
                  color="green",
                  backgroundColor = "#f0eff0")))

>>>>

```{r echo=FALSE, paged.print=TRUE}
reactable(df_submission, 
          defaultPageSize = 4, 
          columns = list(
            link_single_submission_page = colDef(
              cell = function(value) {
                url <- value
                htmltools::tags$a(href = url, 
                                  target = "_blank", 
                                  value)
                },
              width = 150,
              html=TRUE
              )),
          filterable = TRUE,
          bordered=TRUE,
          compact = TRUE,
          style = list(fontSize = "10px"),
          theme = reactableTheme(
            backgroundColor = plot_bg_color,
                filterInputStyle = list(
                  color="green",
                  backgroundColor = plot_bg_color)))
```

@@

```{r include=FALSE}
df_submission <- readr::read_rds(file=here::here("_blog_data", "epidemic_law_submissions",
                                                 "df_submission_150.rds"))

@@

```{r}
tb_text <- reactable(df_submission %>%
            filter(pattern_indicator==TRUE) %>% 
            select(name, date, doc_text),
          defaultPageSize = 4, 
          filterable = TRUE,
          style = list(fontSize = "10px"),
          columns=list(
            name=colDef(width=100),
            date=colDef(width=100),
            doc_text=colDef(minWidth=200)),
          bordered=TRUE,
          compact = TRUE,
          theme = reactableTheme(
            backgroundColor = plot_bg_color,
                filterInputStyle = list(
                  color="green",backgroundColor = plot_bg_color)
          )
          )

@@

```{r echo=FALSE}
reactable(df_collocs,
          bordered=TRUE,
          compact = TRUE,
          style = list(fontSize = "10px"),
          filterable = TRUE,
          theme = reactableTheme(
            backgroundColor = plot_bg_color,
                filterInputStyle = list(
                  color="green",
                  backgroundColor = plot_bg_color)))
```

@@

```{r echo=FALSE}
reactable(head(df_similarity, n = 10^3),
          columns=list(
            cosine=colDef(format=colFormat(digits=4),
                          align="left")),
          bordered=TRUE,
          compact = TRUE,
          style = list(fontSize = "10px"),
          filterable = TRUE,
          theme = reactableTheme(
            backgroundColor = plot_bg_color,
                filterInputStyle = list(
                  color="green",
                  backgroundColor = plot_bg_color)))

### 2021-02-20 _post/2021-01-22-covidconsultationduration/covidconsultationduration.Rmd
css backgroud white

---
title: "Austria's Covid legislation: Duration of parliamentarian consultation period in comparision."
description: |
  A (relative) deep dive into the length of the public consultation period for draft bills in Austria, and whether three days for three pages are actually 'normal'.
date: 01-22-2021
draft: false
author:

@@

```{r chunk_pl_submissions_per_bill, include=FALSE, code_folding=NULL}
pl_submissions_per_bill<- df_consolidated %>% 
  mutate(bill_indicator=case_when(str_detect(title, "Epidemie") & legis_period=="XXVII" ~ "yes",
                                  TRUE ~ as.character("no"))) %>% 
  ungroup() %>% 
  ggplot()+
  labs(title="LEGISLATIVE CONSULTATION PROCESS:<br>Number of filed submissions per bill.",
       subtitle="Note log scale of y-axis.",
       x="Date",
       y="Number of submissions (log scale)",
       caption=caption)+
  geom_segment(aes(x=as.Date("2017-01-01"),
               xend=as.Date("2017-01-01"),
               y=0,
               yend=4000),
               color="grey50")+
  geom_text(label=str_wrap("Introduction of possibility to file electronic submissions via parliament's website",30),
            aes(x=as.Date("2016-06-01"),
            y=6000),
            color="grey50",
            lineheight=0.7,
            check_overlap = T,
            hjust=1,
            vjust=1,
            size=3,
            family="Roboto condensed")+
  geom_jitter_interactive(aes(x=date_end_max,
               y=n_obs_submissions,
               tooltip=glue::glue("{str_wrap(title, 40)}
                                  Number of submissions: {n_obs_submissions}
                                  Bill ID: {bill_id}/{legis_period},

@@

```{r, fig.height=5, echo=F, code_folding=NULL, dev="ragg_png"}
pl_consolidated
```

>>>>

---
title: "Austria's Covid legislation: Duration of parliamentarian consultation period in comparision."
description: |
  A (relative) deep dive into the length of the public consultation period for draft bills in Austria, and whether three days for three pages are actually 'normal'.
date: 02-20 -2021
draft: false
author:

@@

```{r chunk_pl_submissions_per_bill, include=FALSE, code_folding=NULL}
pl_submissions_per_bill<- df_consolidated %>% 
  mutate(bill_indicator=case_when(str_detect(title, "Epidemie") & legis_period=="XXVII" ~ "yes",
                                  TRUE ~ as.character("no"))) %>% 
  ungroup() %>% 
  ggplot()+
  labs(title="LEGISLATIVE CONSULTATION PROCESS:\nNumber of filed submissions per bill.",
       subtitle="Note log scale of y-axis.",
       x="Date",
       y="Number of submissions (log scale)",
       caption=caption)+
  geom_segment(aes(x=as.Date("2017-01-01"),
               xend=as.Date("2017-01-01"),
               y=0,
               yend=4000),
               color="grey50")+
  geom_text(label=str_wrap("Introduction of possibility to file electronic submissions via parliament's website",30),
            aes(x=as.Date("2016-06-01"),
            y=6000),
            color="grey50",
            lineheight=0.7,
            check_overlap = T,
            hjust=1,
            vjust=1,
            size=3,
            family="Roboto condensed")+
  geom_jitter_interactive(aes(x=date_end_max,
               y=n_obs_submissions,
               tooltip=glue::glue("{str_wrap(title, 40)}
                                  Number of submissions: {n_obs_submissions}
                                  Bill ID: {bill_id}/{legis_period},

@@

```{r, fig.height=5, echo=F, code_folding=NULL, dev="svglite"}
pl_consolidated
```
